Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-04-08 paper/ms.tex
new text on correlation functions

\subsection{Selection of the preferred halo mass}

@@

\subsection{Additional observational constraints on the occupation fraction}

@@

As a prediction, we calculate the mean angular correlation function (ACF) for some of the best
models for a mock survey using the match and random methods with 
two different surface areas: $1)$ the full survey (12 subfields) and
$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
(see section XX) . The results for these calculations  are shown 
in figure \ref{figure:correlation_match} (match) and figure
\ref{figure:correlation_random} (random).  The error bars in these figures
represent the standard deviation of the ACF over the subfields. 
We compare these results with the observed ACF in a field of the the SSA22 region
reported by Hayashino et al in 2004.

We can generally observe that the standard deviation of the computed ACF 
in the subfields increase when  increasing $M_{min}$ following the same 
trend as in figure \ref{figure:laes_dist}.Therefore, as the cosmic variance
increase when increasing the halos mass the increment in the ACF standard 
deviation when increasing $M_{min}$ is a direct consequence of cosmic variance.

>>>>

\subsection{Kolmogorov-Smirnov Tests}

@@

\subsection{Constraints from the Angular Correlation Function}

We calculate the mean angular correlation function (ACF) for all
models with $P>0.05$ using the match and random methods. These
correlation functions is calculated over the denseset subfield in all the
mock surveys corresponding to the SSA22 region. These results are
compared against the observations reported by Hayashino et al in 2004
over the same region, which were also performed on the densest field.

Figure \ref{figure:correlation_match} (match) and Figure
\ref{figure:correlation_random} (random) present such comparison.  The
error bars in these figures represent the standard deviation of the
ACF over all the sub-fields.  In general, we observe that the standard
deviation of the computed ACF in the subfields increases with
$M_{min}$ following the same trend as in Figure
\ref{figure:laes_dist}, as a direct consequence of cosmic variance.

The comparison between the simulated and observed ACFs is also done using a
$R^2$ statistic which includes the information on measurement uncertainties

\begin{equation}
R^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
    sim}^2({\theta_i})}, 
\end{equation}

where the sum is done over all the angle values $\theta_i$ where the
ACF has been computed. In Figure XX we plot the integrated
distributions for this $R^{2}$ statistics

\subsection{Observational constraints on the occupation fraction}

@@

As a prediction,
